---
title:  "Building Perceptual Map Using Amazon.com Review Data"
Name: "Po Yi Liu"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#INSTALL AND IMPORT NECESSARY PACKAGES
```{r, message=FALSE, warning=FALSE}
library(jsonlite)
library(R.utils)
library(tidyverse)
library(ggplot2)
```

#*********************************************************************************#
# load data

```{r, message=FALSE, warning=FALSE}
setwd("D:/medium/perceptual map")
review.df <- stream_in(file("Appliances.json.gz"))
meta.df <- stream_in(file("meta_Appliances.json.gz"))
```

```{r}
meta.df <- meta.df[,c("asin","brand","category")] 
```


#Merge datasets by ASIN 
```{r, message=FALSE, warning=FALSE}
data <- merge(meta.df, review.df, by="asin")
```



#*********************************************************************************#
# OBTAIN THE LIST OF BRANDS TO BUILD PERCEPTUAL MAP

#dropping observations without brand information, combining the same brands with various name variances, etc.
#Note what's needed to do is dependent of the product category
```{r, message=FALSE, warning=FALSE}
data <- data%>%
  filter(!is.na(brand))
```



#Find the top 20 brands in terms of total number of reviews
```{r, message=FALSE, warning=FALSE}
brands <- data%>%
  filter(grepl('Range Parts & Accessories', category))%>%
  select(brand) %>%
  group_by(brand) %>%
  count()%>%
  arrange(desc(n))%>%
  na.omit() %>%
  ungroup() %>%
  top_n(20, wt = n)

top_20_brands <- brands$brand

```


#*********************************************************************************#
# CONSTRUCT THE SIMILARITY MATRIX

#Define function "computeLift"
```{r, message=FALSE, warning=FALSE}
computeLift <- function(data, brands){
    
  # Initialize a matrix to store the cooccurrence results
  lift <- data.frame(matrix(NA, nrow=length(brands), ncol=length(brands)))
  rownames(lift) <- brands
  colnames(lift) <- brands
  
  # Initialize an array to store the occurrences, with the i th element being the occurrences of brand i
  arr_occ <- c()
  
  # Initialize an array to store the co-occurrences, with the i*j th element being the co-occurrences of brand i and brand j
  arr_coocc <- c()
  
  for (i in seq_along(brands)) {
    
    # In the outer loop, get the occurrences of brand i, and append it to the end of arr_occ
    b1 <- brands[i]
    # Detect the occurrences of b1 in review text
    flag_1_rev <- str_detect(data$reviewText, b1)
    # Detect whether the associated brand of the review is b1
	  # We assume any nrand i reviews is a mention of the brand, even the brand name is not explicitly mentioned in review text.
    flag_1_brand <- str_detect(data$brand, b1)
    
    # However, the str_detect function will return NA if the string is empty
    # Set NAs in the `flag`, a boolean array, to False
    flag_1_rev[is.na(flag_1_rev)] <- F
    flag_1_brand[is.na(flag_1_brand)] <- F
    
    # Combine the two flags with 'OR' condition
	  # As such, flag_1 flags all reviews that "mentions" brand i.
    flag_1 <- flag_1_rev | flag_1_brand
      
    arr_occ <- c(arr_occ, sum(flag_1))
    	
    for (j in seq_along(brands)){
      # In the inner loop, first get the occurrences of brand j.
	  # Then get the co-occurrences of brand i and brand j, and append it to the end of arr_coocc
	  
	  # First, get the occurrences of brand j
      b2 <- brands[j]
      # Detect the occurrences of b2 in review text
      flag_2_rev <- str_detect(data$reviewText, b2)
      # Detect whether the review is under the product of b2
      flag_2_brand <- str_detect(data$brand, b2)
      
      # However, the str_detect function will return NA if the string is empty
      # Replace NA with FALSE
      flag_2_rev[is.na(flag_2_rev)] <- F
      flag_2_brand[is.na(flag_2_brand)] <- F
      
      # Combine the flags of b2 with 'OR' condition
	  # As such, flag_2 flags all reviews that "mentions" brand j.
      flag_2 <- flag_2_rev | flag_2_brand
      
      # get the index of co-occurrences of with "AND" condition
      arr_coocc <- c(arr_coocc, sum(flag_2 & flag_1))
      
    }
  }

  # calculate lift #  
  # Lift is a metric defined as the ratio of the actual co-occurrence of two terms to the frequency with which we would expect to see them together.
  # The lift between terms A and B can be calculated as:
  # Lift(A,B)= (P(A,B))/(P(A)×P(B))
  # where P(X) is the probability of occurrence of term X in a given review, and P(X, Y) is the probability that both X and Y appear in a given review
  
  # loop over each cell of `lift` table by rows and columns 
  # iterate over rows, indexed by i
  for (i in 1:nrow(lift)){
    # loop over columns, indexed by j
    for (j in 1:ncol(lift)) {
      # IF:
      #  (1) the cell indexed is on the diagonal line, OR
      #  (2) P(A) is zero, OR
      #  (3) P(B) is zero
      # THEN skip the loop because the denominator will be zero
      if (i == j | arr_occ[i] == 0 | arr_occ[j] == 0) {
        next
      # Calculate lift with P(A, B)/(P(A)*P(B))
      } else {
		PAB <- arr_coocc[(i-1)*nrow(lift)+j]/nrow(data)
		PA <- arr_occ[i]/nrow(data)
		PB <- arr_occ[j]/nrow(data)
        lift[i, j] = PAB / (PA * PB)
      }
      
    }
  }
  return(lift)
}

```


```{r, message=FALSE, warning=FALSE}
lift <- data.frame(matrix(NA, nrow=length(top_20_brands), ncol=length(top_20_brands)))
  rownames(lift) <- top_20_brands
  colnames(lift) <- top_20_brands
  
  # Initialize an array to store the occurrences, with the i th element being the occurrences of brand i
  arr_occ <- c()
  
  # Initialize an array to store the co-occurrences, with the i*j th element being the co-occurrences of brand i and brand j
  arr_coocc <- c()
  
for (i in seq_along(top_20_brands)) {
    
    # In the outer loop, get the occurrences of brand i, and append it to the end of arr_occ
  b1 <- top_20_brands[i]
    # Detect the occurrences of b1 in review text
  flag_1_rev <- str_detect(data$reviewText, b1)
    # Detect whether the associated brand of the review is b1
	# We assume any nrand i reviews is a metion of the brand, even the brand name is not explicitly mentioned in review text.
  flag_1_brand <- str_detect(data$brand, b1)
    
    # However, the str_detect function will return NA if the string is empty
    # Set NAs in the `flag`, a boolean array, to False
  flag_1_rev[is.na(flag_1_rev)] <- F
  flag_1_brand[is.na(flag_1_brand)] <- F
    
    # Combine the two flags with 'OR' condition
	# As such, flag_1 flags all reviews that "mentions" brand i.
  flag_1 <- flag_1_rev | flag_1_brand
      
  arr_occ <- c(arr_occ, sum(flag_1))
    	
  for (j in seq_along(top_20_brands)){
      # In the inner loop, first get the occurrences of brand j.
	  # Then get the co-occurrences of brand i and brand j, and append it to the end of arr_coocc
	  
	  # First, get the occurrences of brand j
    b2 <- top_20_brands[j]
      # Detect the occurrences of b2 in review text
    flag_2_rev <- str_detect(data$reviewText, b2)
      # Detect whether the review is under the product of b2
    flag_2_brand <- str_detect(data$brand, b2)
      
      # However, the str_detect function will return NA if the string is empty
      # Replace NA with FALSE
    flag_2_rev[is.na(flag_2_rev)] <- F
    flag_2_brand[is.na(flag_2_brand)] <- F
      
      # Combine the flags of b2 with 'OR' condition
	  # As such, flag_2 flags all reviews that "mentions" brand j.
    flag_2 <- flag_2_rev | flag_2_brand
      
      # get the index of co-occurrences of with "AND" condition
    arr_coocc <- c(arr_coocc, sum(flag_2 & flag_1))
      
  }
}
```

```{r, message=FALSE, warning=FALSE}
lift <- computeLift(data, top_20_brands)
#write_csv(lift, "lift.csv") 

```


#*********************************************************************************#

# CONVERT SIMILARITY MATRIX TO DISSIMILARITY MATRIX
#Define function "convertSim"
```{r, message=FALSE, warning=FALSE}
convertSim <- function(SimilarityMatrix) {
		
	# Initialize the dissimilarity matrix
	DissMat <- data.frame(matrix(NA, nrow=nrow(SimilarityMatrix), ncol=ncol(SimilarityMatrix)))

	# Use a nested loop to iterate over the similarity matrix to change extremely small values to our lower bound
	# we believe that the 0.00001 is small enough and the 9999999 is large enough to represent the ultimate dissimilarity
	for (i in 1:nrow(SimilarityMatrix)) {
		for (j in 1:ncol(SimilarityMatrix)) {
			if(i == j){
			# Assign zeros to the diagonal line--the dissimilarity of the pair of same brand is zero
			DissMat[i, j] <- 0
			next
			} else if (is.na(SimilarityMatrix[i, j])){
				# if the cell is NA, the pair of brands has never been mentioned together, so very dissimilar to each other.
				# For this case, assign lower bound to SimilarityMatrix and 9999999 to DissMat
				DissMat[i, j] <- 9999999
				next
			} else if (abs(SimilarityMatrix[i, j]) <= 0.00001) {
				# if the cell is smaller than the lower bound, assign lower bound to it and 9999999 to DissMat
				DissMat[i, j] <- 9999999
				next
			}
		}
	}

	# Calculate dissimilarity of other cells
	for (i in 1:nrow(SimilarityMatrix)) {
	  for (j in 1:ncol(SimilarityMatrix)) {
		if (is.na(DissMat[i, j])) {
		  DissMat[i, j] <- round(1/SimilarityMatrix[i, j],4)
		}
	  }
	}

	# assign indexes to the dissimilarity matrix
	rownames(DissMat) <- rownames(SimilarityMatrix)
	colnames(DissMat) <- colnames(SimilarityMatrix)

	return(DissMat)
}

```


```{r, message=FALSE, warning=FALSE}
dissLift <- convertSim(lift)
```


#*********************************************************************************#

# BUILD PERCEPTUAL MAP
#Define function "mds_plot"
```{r, message=FALSE, warning=FALSE}
mds_plot <- function(DissimilarityMatrix, title = "MDS Perceptual Map Based on Amazon.com Review Data", 
                     c1 = "Coordinate 1", c2 = "Coordinate 2") {
					 
	# get the 2-dimensional MDS scale
  dissLift.mat <- data.matrix(dissLift)
	DissMatrix.mds <- cmdscale(dissLift.mat, eig=TRUE, k=2)
	
	# DissMatrix.mds is a list
	result <- data.frame(DissMatrix.mds$points)
	colnames(result) = c("Coordinate1", "Coordinate2")
	
	# Plot solution
	p <- ggplot(data = result, aes(x= Coordinate1, y = Coordinate2)) +
	  geom_text(label = rownames(result)) +
	  ggtitle(title) +
	  labs(x = c1, y = c2)

	return(list("mds_plot" = p, "DissLift" = DissimilarityMatrix))
}

```


# get the MDS plot using the self-defined function
```{r, message=FALSE, warning=FALSE}
mds <- mds_plot(dissLift)
mds$mds_plot
```


